Towards a Practical Face Recognition System: \\ Robust Alignment and Illumination by Sparse Representation

### 2011-03-31 faces_system.tex
Minor change to make a sentence read better.

%\begin{table}
%\caption{Recognition rates on the Multi-PIE database for
%different pairings of alignment and recognition stages.}
%\vspace{-.2in} \centerline{
%\begin{tabular}{|c|c|c|c|c| } \hline
%Recognition rate & Session 2 & Session 3 & Session 4  \\
%\hline
%LDA($d/m/i$) & 5.1 / 49.4 / 91.0\% & 5.9 / 44.3 / 89.9\% & 4.3 / 47.9 / 88.1\% \\
%\hline
%NN($d/m/i$) & 26.4 / 67.3 / 73.5\% & 24.7 / 66.2 / 69.6\% & 21.9 / 62.8 / 69.3\% \\
%\hline
%NS($d/m/i$) & 30.8 / 77.6 / 84.5\% & 29.4 / 74.3 / 82.3\% & 24.6 / 73.4 / 81.4\% \\
%\hline
%LBP($d/m/i$) & 39.9 / 93.3 / {\bf 95.2}\% & 38.1 / 91.2 / {\bf 94.7}\% & 33.9 / 92.9 / {\bf 93.5}\% \\
%\hline
%Algorithm 1 & 93.9\% & 93.8\% & 92.3\% \\
%\hline
%\end{tabular}
%\label{tab:MultiPIE-recognition} }\vspace{-.4in}
%\end{table}

@@

In addition, although our algorithm is not designed for
recognition when there is only a single gallery image per user,
we compare its performance with LBP within this setting for
completeness. For this experiment, we use the FERET dataset
\cite{phillips1998feret}, which contains five standard
partitions: `fa' is the gallery containing 1196 frontal images
of 1196 subjects, and `fb', `fc', `dup1' and `dup2' are four
sets of probe images. The testing sets differ from the training
in facial expression (`fb'), illumination (`fc'), aging (`dup1'
) and long aging (`dup2'). In fact, except for `fb', we notice
significant changes of illumination in all the other three test
sets. For the training, we again crop and normalize the face
region from each original image to an $80\times 60$ window
using manually marked eye coordinates \cite{Deng2010-PR}. In
Table~\ref{tab:FERET-recognition}, we report the performance of
our algorithm on the four test sets, with input directly
obtained from the Viola and Jones' detector. We also report the
performance of LBP with the same three types of input as before
in Table~\ref{tab:FERET-recognition}, where we use letters
``$d$'', ``$m$'' and ``$i$'' to indicate face detector, manual
alignment and our iterative alignment algorithm, respectively.

>>>>

@@

In addition, although our algorithm is not designed for
recognition when there is only a single gallery image per user,
we compare its performance with LBP within this setting for
completeness. For this experiment, we use the FERET dataset
\cite{phillips1998feret}, which contains five standard
partitions: `fa' is the gallery containing 1196 frontal images
of 1196 subjects, and `fb', `fc', `dup1' and `dup2' are four
sets of probe images. The testing sets differ from the training
in facial expression (`fb'), illumination (`fc'), aging (`dup1'
) and long aging (`dup2'). In fact, except for `fb', we notice
significant changes of illumination in all the other three test
sets. For the training, we again crop and normalize the face
region from each original image to an $80\times 60$ window
using manually marked eye coordinates \cite{Deng2010-PR}. In
Table~\ref{tab:FERET-recognition}, we report the performance of
our algorithm on the four test sets, with input directly
obtained from the Viola and Jones' detector. We also report the
performance of LBP with the same three types of input as before:
we use letters
``$d$'', ``$m$'', and ``$i$'' to indicate face detector, manual
alignment, and our iterative alignment algorithm, respectively.
